Borel regularity for ODEs and Thimble Integrals

### 2024-01-19 exp-resurgence.tex
Updates from Overleaf

\theoremstyle{definition}
\newtheorem{defn}{Definition}
%%\theoremstyle{plain}
%%\newtheorem{prop}{Proposition}

@@

\newtheorem{definition}{Definition}[section]
\newtheorem{remark}[definition]{Remark}
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}[definition]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[definition]{Lemma}
%\newtheorem{conjecture}[definition]{Conjecture}
\newtheorem{claim}[definition]{Claim}
%\newtheorem{exercise}[definition]{Exercise}
\newtheorem*{notation*}{Notation}

@@

\begin{brainstorm}
    \item Section~\ref{borel_reg-ODE} and maybe other subsections--revise the proof of the main result for ODE taking into account the results in our paper
    \item Do flagged revisions in Section~\ref{borel-reg-thimble}
    \item Section~\ref{contour-argument-AL}---revise the general contour argument
    \item Revise Section 2, using the formalism of $\singexp{\sigma}{\Lambda}(\Omega)$
    \begin{itemize}
    \item Replace formalism in Section~\ref{reg-decay}
    \end{itemize}
    \item Check which examples are still in the framework of our theorem
    \begin{itemize}
    \item Start a storage document for shelved examples
    \end{itemize}
    \item Section~\ref{resurgence-AL}---Draw intersection points figure
    \item Section~\ref{sec:mod-bessel-lift}---pin down contour
    \item Explain contour figure in Airy example [explain what the regions indicate and what the color]
    \begin{itemize}
    \item Figure out how to release source code. How much do we need to clean it up? Is it okay that it relies on Shadertoy?
    \end{itemize}
    \item Look at ``Plan of the paper'' appendix and confirm that we've included everything we want
    \begin{itemize}
    \item Put future goals in storage document
    \end{itemize}
    \item Veronica doesn't like $\gamma_z$ as notation for Hankel contour. I'll suggest $\mathcal{H}_{1,z}$ where $1$ is the point where the path is centered. 
\end{brainstorm}

@@

%We can use the Laplace transform to convert $\mathcal{P}$ into a family of integral operators $\hat{\mathcal{P}}_\upsilon$ parameterized by the point $\zeta = \upsilon$ on the position domain.
\color{Maroon}
\begin{theorem}\label{thm:borel_reg_ODE}
Choose a root $-\alpha$ of $P$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. Equation~\eqref{eqn:standard ODE} has a unique solution $\Psi_\alpha$ in the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\textcolor{orange}{[figure out where to put definition]}. That solution is Borel regular.
\end{theorem}
\begin{corollary}\label{cor:borel_reg_ODE}
For each root $-\alpha$ of $P$, Equation~\eqref{eqn:standard ODE} has a formal solution in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$, which is unique up to scaling. That solution is Borel summable, and its Borel sum is a constant multiple of $\Psi_\alpha$.
\end{corollary}
\color{black}
\begin{theorem}[see Theorem \ref{thm2-dim}]\label{thm2}
The formal frame of solutions $\tilde{\Psi}_j$ is Borel summable \textcolor{orange}{[summability is the strongest part of the result]} and its Borel sum is proportional to $\Psi_j$. In fact, $\Psi_j$ is a Borel regular solution of \eqref{eqn:standard ODE}. \textcolor{orange}{[Alternate statement: look in Sauzin or Delabaere to get uniqueness of formal solution.]} \textcolor{orange}{[Split into theorem, which shows existence of Borel regular frame, and corollary, which shows that this implies a certain frame of formal solutions is Borel-summable and sums to actual solutions.]}
\end{theorem}
%
We summarize the main steps of the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE} (the rigorous proofs are given in Section~\ref{borel_reg-ODE}). On the right-hand side of the diagram, we have the formal solution $\series{\Psi }_\alpha\in e^{-\alpha z}z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$ and its Borel transform $\series{\psi}_\alpha$. %Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.

@@

%\subsection{Stokes phenomenon}
%\begin{itemize}
%\item For Bessel functions, we can see explicitly how solutions jump when the Laplace transform angle crosses a critical value.
%\item The jump comes from the branch cut difference identity for hypergeometric functions.
%\item Possible interpretation of the Stokes factors as intersections numbers in Morse--Novikov theory \textbf{[ask Maxim]}
%\end{itemize}
\subsection{Plan of the paper}
The paper is organized as follows: Section~\ref{sec:Laplace-Borel-general} is devoted to define the new geometric picture of the Borel and Laplace transform. The reader who is not familiar with the formalism of Borel and Laplace transforms might start with Sections \ref{reg-decay}, the beginning of Section \ref{sec:geometry_borel},  \ref{sec:formal_borel}, and \ref{properties Borel transform}. Then, Section~\ref{sec:proof_main_results} contains proofs of the main results: Theorem~\ref{thm2} and Theorem~\ref{thm:maxim}. Finally, in Section~\ref{sec:examples} we give a detailed treatment of different examples both from the ODE perspective and from the thimble integral one. 
We include two appendices: the first one (Appendix~\ref{airy-appendix}) contains a detailed treatment of the Airy example, and it is recommended for readers less familiar to the subject. The second one, Appendix~\ref{apx:generalities_ODEs}, reviews the main aspects of \cite{reg-sing-volterra}.  
%
\subsection{Acknowledgements}
This paper is a result of the ERC-SyG project, Recursive and Exact New Quantum Theory (ReNewQuantum) which received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 810573.

@@

%\textcolor{orange}{hyperasymptotics \cite{Berry_Howls,Berry1991,Howls97,Howls}}
%\color{DarkTurquoise}
%These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22}, Berry and Howls \cite{Berry_Howls} and Sternin and Shatalov \cite[Theorem 3.9 and 3.10]{sternin1995borel}. In addition, the study of thimble integrals plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities. Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,pham1988resurgence}.
%\color{black}
%%Our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture \cite{Fenyes-ihes-lecture}). In a nutshell, we use that thimble integrals are generalized Laplace transforms, to show they are indeed Borel regular functions.  
%     
\section{The Laplace and Borel transforms}\label{sec:Laplace-Borel-general}
\subsection{The geometry of the Laplace transform}
Classically, the Laplace transform turns functions on the position domain into functions on the frequency domain. In the study of Borel summation and resurgence, it's useful to see the position domain as a {\em translation surface} $B$, and the frequency domain as one of its cotangent spaces. Roughly speaking, the Laplace transform lifts holomorphic functions on $B$ to holomorphic functions on $T^* B$.
%
\subsubsection{Translation surfaces, briefly}
%
A translation surface is a Riemann surface $B$ carrying a holomorphic $1$-form $\lambda$~\cite{zorich2006flat}. A translation chart is a local coordinate $\zeta$ with $d\zeta = \lambda$. The standard metric on $\C$ pulls back along translation charts to a flat metric on $B$, with a conical singularity of angle $2\pi n$ wherever $\lambda$ has a zero of order $n-1 > 0$. We'll require $B$ to be finite-type and $\lambda$ to have a pole at each puncture. This kind of translation surface has a ``cylindrical end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $n-1 < -1$~\cite[Section 2.5]{gupta2013meromorphic} (or cite Aaron's article, which will hopefully present the same background in the translation surface context).
\begin{figure}[ht]
    \centering
    %\includegraphics{}
    \caption{On the left an example of translation surface with ``cylindrical end''. On the right, an example of translation surface with  ``$|2n|$-planar end''. }
    \label{fig:translation_surface}
\end{figure}
%
\subsubsection{Direction}\label{transl:dir}
%
The translation structure gives $B$ a notion of direction as well as distance. Away from the zeros of $\lambda$, which we'll call {\em branch points}, we can talk about moving upward, rightward, or at any angle, just as we would on $\C$. At a branch point of cone angle $2\pi n$, we can also talk about moving upward, rightward, or at any angle in $\R/2\pi\Z$, but here there are $n$ directions that fit each description. To make this more concrete, note that around any point $b \in B$, there's a unique holomorphic function $\zeta_b$ that vanishes at $b$ and has $d\zeta_b = \lambda$. \textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] there's a unique translation parameter $\zeta_b$ that vanishes at $b$.} This function is a translation chart when $b$ is an ordinary point, and an $n$-fold branched covering when $b$ is a branch point of cone angle $2\pi n$. In either case, $\zeta_b \in e^{i\theta} [0, \infty)$ is a ray or a set of rays leaving $b$ at angle $\theta \in \R/2\pi\Z$.
%

Near each branch point $b$, let's fix a coordinate $\omega_b$ with $\zeta_b = \tfrac{1}{n} \omega_b^n$, where $2\pi n$ is the cone angle at $b$. This lets us label each direction at $b$ with an ``extended angle'' in $\R/2\pi n\Z$. Of course, there are $n$ different choices for $\omega_b$.
%
\subsubsection{Frequency}\label{transl-freq}
%
The translation structure also gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$. At an ordinary point, we can define $z$ simply as the map
\begin{align*}
z \maps T^*B_b & \to \C \\
\lambda\big|_b & \mapsto 1.
\end{align*}
To get a definition that generalizes to branch points, though, it's worth taking a fancier point of view. Recall that $T^*B_b = \van_b / \van_b^2$, where $\van_b$ is the ideal of holomorphic functions that vanish at $b$. Observing that $(f + \van_b)^n$ lies within $f^n + \van_b^{n+1}$ for any $f \in \van_b$, we can identify $T^*B_b^{\otimes n}$ with $\van_b^n / \van_b^{n+1}$ for $n \ge 1$. When $b$ is an ordinary point, the function $\zeta_b$ defined in Section~\ref{transl:dir} represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda\big|_b$. In general, $\zeta_b$ represents a nonzero element of $\van_b^n / \van_b^{n+1}$, where $2\pi n$ is the cone angle at $b$. We define $z$ as the isomorphism
\begin{align*}
z \maps \van_b^n / \van_b^{n+1} & \to \C \\
\zeta_b + \van^{n+1} & \mapsto 1.
\end{align*}
When $b$ is a branch point, the coordinate $\omega_b$ we chose in Section~\ref{transl:dir} gives us an isomorphism
\begin{align*}
w_b \maps T^*B_b & \to \C \\
\omega_b + \van^2 & \mapsto 1
\end{align*}
that makes the diagram
\begin{center}
\begin{tikzcd}
T^*B_b^{\otimes n} \arrow[r,"z"] & \C \\
T^*B_b \arrow[u,"\blankbox^n"] \arrow[r,"w"'] & \C \arrow[u,"\blankbox^n"']
\end{tikzcd}
\end{center}
commute.
\subsubsection{Boundary}
\textcolor{red}{\textbf{Discuss the visual boundary, citing Lemma~3.1 of Dankwart's thesis \textit{On the large-scale geometry of flat surfaces} for the description of geodesics.}}
%
\subsubsection{The Laplace transform over an ordinary point}\label{laplace:ordinary}
Pick a local holomorphic function $\zeta$ on $B$ with $d\zeta = \lambda$, and an extended angle $\theta \in \R$. \textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] Pick a translation parameter $\zeta$.} The {\em Laplace transform} $\laplace_\zeta^\theta$ turns a local holomorphic function $f$ on $B$ into a local holomorphic function on $T^*B$. When $b \in B$ is an ordinary point, $\laplace_\zeta^\theta f$ is defined on $T_b^*B$ by the formula
\begin{equation}\label{laplace:int}
\laplace_\zeta^\theta f\big|_b = \int_{\Gamma_b^\theta} e^{-z\zeta} f\,d\zeta,
\end{equation}
where $z$ is the frequency function and $\Gamma_b^\theta$ is the ray that leaves $b$ at angle $\theta$. We’ll use the shorthand $\laplace_{\zeta, \beta}^\theta f := \laplace_\zeta^\theta f \big|_{\zeta = \beta}$ throughout this document.

@@

\subsection{The Laplace transform: analytic version}\label{sec:laplace_analytic}
\subsubsection{Regularity and decay properties}\label{reg-decay}
Let $\Omega_\alpha \subset B$ be an open, simply connected set that touches but does not contain $\zeta=\alpha$ (see Figure \ref{Fig:domain}). Suppose $\Omega_\alpha$ contains the ray $\Gamma_{\zeta,\alpha}^\theta$. In \cite{reg-sing-volterra} we introduce the function space $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ of holomorphic functions on $\Omega_\alpha$ which are uniformly of exponential type $\Lambda$ and blow up like $|\zeta|^\sigma$ as $\zeta$ approaches $\alpha$. When $\sigma>-1$, the singularity at $\zeta=\alpha$ is integrable. Hence, the Laplace transform $\laplace_{\zeta, \alpha}^\theta$ turns elements of $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ into well-defined holomorphic functions on the half-plane $\Re(e^{i\theta} z) > 0$ in the fiber $T_{\zeta=\alpha}^*B$~\cite[Section  5.6]{diverg-resurg-i}.
%Let's say a function $f$ is in $O_{\zeta, \alpha \leftarrow}(g)$ or $O_{\zeta, \alpha \rightarrow}(g)$, respectively, if $|f| \lesssim g$ on some neighborhood of the starting point or infinite end of $\Gamma_{\zeta, \alpha}$. A function is {\em subexponential} along $\Gamma_{\zeta, \alpha}$ if it's in $O_{\zeta, \alpha \rightarrow}(e^{c\zeta})$ for all $c > 0$ \textcolor{magenta}{[shall we write in formula?]}. Let $\mathcal{E}_{\zeta, \alpha}$ be the space of functions that are subexponential on $\Gamma_{\zeta, \alpha}$, integrable at the starting point, and locally integrable throughout. If $f$ is in $\mathcal{E}_{\zeta, \alpha}$, then $\laplace_{\zeta, \alpha} f$ is well-defined and holomorphic for $\Re(z) > 0$ on the part of $T^*B$ that lies over $\Gamma_{\zeta, \alpha}$~\cite[Section  5.6]{diverg-resurg-i}.

%%On $\Omega_\alpha^\varepsilon$, by construction, the angle $\arg(\zeta)$ is more than $\pi + \varepsilon/2$ away from the asymptotic directions of $\textcolor{magenta}{\Lambda}$. Hence, on $\Omega_\alpha^\varepsilon \times \textcolor{magenta}{\Lambda}$, we have
%%\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\lambda' - \sin(\varepsilon/2)\,|t|\big) \]
%%for some constant $\lambda' \in \R$. It follows that
%%\begin{align*}
%%\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F\right| & \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\lambda' - \sin(\varepsilon)\,|t|\right)} \Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma} \|F\|_{\sigma, \Lambda}\,dt \\
%%& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma}}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon)\,t}\,dt \\
%%& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma}}{2 \pi}\,\frac{2}{|\zeta_\alpha| \sin(\varepsilon)}
%%\end{align*}
\textcolor{orange}{[Oops, looks like we can't keep $\Delta$ constant along the integration path if we want to recover something with a $|\zeta_\alpha|^{\sigma-1}$ singularity.]}
\color{RoyalBlue}
\textcolor{orange}{[We might be able to remove the decay properties completely!]} The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}^\theta$ control the asymptotics of $\laplace_{\zeta, \alpha}^\theta f$ at the infinite end of $\Gamma_{z, 0}$. Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest. In addition, we'll set $\theta=0$ to keep the notation simpler, but the results hold for every angle $\theta$. Let $F = \laplace_{\zeta, 0} f$. Equation~1.8 of \cite{laplace-tfm} shows\footnote{The argument cited still works in our generality. For holomorphic $f$, one can also use \cite[Equation 1.5]{sternin1995borel}.} that
\[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
More generally, for $\sigma > -1$ \textcolor{magenta}{[prove or cite]},
\[ f \in O_{\zeta, 0 \leftarrow}(\zeta^\sigma) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z^{1 + \sigma}}\right). \]
Exact power law asymptotics relate similarly \textcolor{magenta}{[prove or cite]}:
\[ f \sim \zeta^\tau \text{ at the start of } \Gamma_{\zeta, 0} \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at the end of } \Gamma_{z, 0}. \]
\textcolor{magenta}{[The big-$O$ asymptotics dictionary is interesting, but we might not need it. Consider dropping.]}
\subsubsection{Properties of the Laplace transform}
%\subsubsection{Change of translation chart}\label{translation}

@@

Let $\zeta_\alpha$ be a coordinate on $B$ so that $\zeta = \alpha + \zeta_\alpha$, then

@@

    \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi.

@@

@@

\laplace_{\zeta, a} \varphi & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\

>>>>

@@

% theorem environments
\theoremstyle{definition}
\newtheorem{defn}{Definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{remark}[definition]{Remark}
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}[definition]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[definition]{Lemma}
%\newtheorem{conjecture}[definition]{Conjecture}
\newtheorem{claim}[definition]{Claim}
%\newtheorem{exercise}[definition]{Exercise}
\newtheorem*{notation*}{Notation}

@@

\begin{brainstorm}
    \item Section~\ref{borel_reg-ODE} and maybe other subsections--revise the proof of the main result for ODE taking into account the results in our paper
    \item Do flagged revisions in Section~\ref{borel-reg-thimble}
    \item Section~\ref{contour-argument-AL}---revise the general contour argument
    \item Revise Section 2, using the formalism of $\singexp{\sigma}{\Lambda}(\Omega)$
    \begin{itemize}
    \item Replace formalism in Section~\ref{sec:reg-decay}
    \end{itemize}
    \item Check which examples are still in the framework of our theorem
    \begin{itemize}
    \item Start a storage document for shelved examples
    \end{itemize}
    \item Section~\ref{resurgence-AL}---Draw intersection points figure
    \item Section~\ref{sec:mod-bessel-lift}---pin down contour
    \item Explain contour figure in Airy example (explain what the regions indicate and what the color)
    \begin{itemize}
    \item Figure out how to release source code. How much do we need to clean it up? Is it okay that it relies on Shadertoy?
    \end{itemize}
    \item Look at ``Plan of the paper'' appendix and confirm that we've included everything we want
    \begin{itemize}
    \item Put future goals in storage document
    \end{itemize}
    \item Veronica doesn't like $\gamma_z$ as notation for Hankel contour. I'll suggest $\mathcal{H}_{1,z}$ where $1$ is the point where the path is centered. 
\end{brainstorm}

@@

%We can use the Laplace transform to convert $\mathcal{P}$ into a family of integral operators $\hat{\mathcal{P}}_\upsilon$ parameterized by the point $\zeta = \upsilon$ on the position domain.
\color{Maroon}
\begin{theorem}\label{thm:borel_reg_ODE}
Choose a root $-\alpha$ of $P$. Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. Equation~\eqref{eqn:standard ODE} has a unique solution $\Psi_\alpha$ in the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\textcolor{orange}{[figure out where to put definition]}. That solution is Borel regular.
\end{theorem}
\textcolor{violet}{If you prefer to work in the analytic world, you can use this result to prove the existence and Borel summability of special formal transmonomial solutions.}
\begin{corollary}\label{cor:borel_reg_ODE}
For each root $-\alpha$ of $P$, Equation~\eqref{eqn:standard ODE} has a formal solution in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$, which is unique up to scaling. That solution is Borel summable, and its Borel sum is a constant multiple of $\Psi_\alpha$.
\end{corollary}
\textcolor{violet}{On the other hand, if you prefer to work in the formal world, you can use Theorem~\ref{thm:borel_reg_ODE} to show that the Poincar\'{e} solutions are Borel summable. See Section~\ref{sec:new-summability-proof}.}
\textcolor{violet}{[In another section, do the ``mirror image'' argument. Use the Poincar\'{e} algorithm to construct a formal transmonomial solution in the classical way. Use the Ramis index theorem to show that it's Gevrey-$1$, and then then use our existence and uniqueness result for regular singular Volterra equations to show that it's not only Gevrey-$1$, but in fact Borel summable.]}
%%The formal solution whose existence is shown in Corollary~\ref{cor:borel_reg_ODE} is the Poincar\'{e} solution.
%%\begin{corollary}
%%\textcolor{orange}{[The Poincar\'{e} solution is Borel summable.]}
%%\end{corollary}
\color{black}
\textcolor{Violet}{[This is sort of a mirror image of the Ramis index theorem?]}
\begin{theorem}[see Theorem \ref{thm2-dim}]\label{thm2}
The formal frame of solutions $\tilde{\Psi}_j$ is Borel summable \textcolor{orange}{[summability is the strongest part of the result]} and its Borel sum is proportional to $\Psi_j$. In fact, $\Psi_j$ is a Borel regular solution of \eqref{eqn:standard ODE}. \textcolor{orange}{[Alternate statement: look in Sauzin or Delabaere to get uniqueness of formal solution.]} \textcolor{orange}{[Split into theorem, which shows existence of Borel regular frame, and corollary, which shows that this implies a certain frame of formal solutions is Borel-summable and sums to actual solutions.]}
\end{theorem}
%
We summarize the main steps of the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE} (the rigorous proofs are given in Section~\ref{borel_reg-ODE}). On the right-hand side of the diagram, we have the formal solution $\series{\Psi }_\alpha\in e^{-\alpha z}z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$ and its Borel transform $\series{\psi}_\alpha$. %Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.

@@

%\subsection{Stokes phenomenon}
%\begin{itemize}
%\item For Bessel functions, we can see explicitly how solutions jump when the Laplace transform angle crosses a critical value.
%\item The jump comes from the branch cut difference identity for hypergeometric functions.
%\item Possible interpretation of the Stokes factors as intersections numbers in Morse--Novikov theory \textbf{[ask Maxim]}
%\end{itemize}
\subsection{Plan of the paper}
The paper is organized as follows: Section~\ref{sec:Laplace-Borel-general} is devoted to define the new geometric picture of the Borel and Laplace transform. The reader who is not familiar with the formalism of Borel and Laplace transforms might start with Sections \ref{sec:reg-decay}, the beginning of Section \ref{sec:geometry_borel},  \ref{sec:formal_borel}, and \ref{properties Borel transform}. Then, Section~\ref{sec:proof_main_results} contains proofs of the main results: Theorem~\ref{thm2} and Theorem~\ref{thm:maxim}. Finally, in Section~\ref{sec:examples} we give a detailed treatment of different examples both from the ODE perspective and from the thimble integral one. 
We include two appendices: the first one (Appendix~\ref{airy-appendix}) contains a detailed treatment of the Airy example, and it is recommended for readers less familiar to the subject. The second one, Appendix~\ref{apx:generalities_ODEs}, reviews the main aspects of \cite{reg-sing-volterra}.  
%
\subsection{Acknowledgements}
This paper is a result of the ERC-SyG project, Recursive and Exact New Quantum Theory (ReNewQuantum) which received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 810573.

@@

%\textcolor{orange}{hyperasymptotics \cite{Berry_Howls,Berry1991,Howls97,Howls}}
%\color{DarkTurquoise}
%These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22}, Berry and Howls \cite{Berry_Howls} and Sternin and Shatalov \cite[Theorem 3.9 and 3.10]{sternin1995borel}. In addition, the study of thimble integrals plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities. Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,pham1988resurgence}.
%\color{black}
%%Our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture \cite{Fenyes-ihes-lecture}). In a nutshell, we use that thimble integrals are generalized Laplace transforms, to show they are indeed Borel regular functions.  
%     
\section{The Laplace and Borel transforms}\label{sec:Laplace-Borel-general}
\subsection{The geometry of the Laplace transform}
Classically, the Laplace transform turns functions on the position domain into functions on the frequency domain. In the study of Borel summation and resurgence, it's useful to see the position domain as a {\em translation surface} $B$, and the frequency domain as one of its cotangent spaces. Roughly speaking, the Laplace transform lifts holomorphic functions on $B$ to holomorphic functions on $T^* B$.
%
\subsubsection{Translation surfaces, briefly}
%
A translation surface is a Riemann surface $B$ carrying a holomorphic $1$-form $\lambda$~\cite{zorich2006flat}. A translation chart is a local coordinate $\zeta$ with $d\zeta = \lambda$. The standard metric on $\C$ pulls back along translation charts to a flat metric on $B$, with a conical singularity of angle $2\pi n$ wherever $\lambda$ has a zero of order $n-1 > 0$. We'll require $B$ to be finite-type and $\lambda$ to have a pole at each puncture. This kind of translation surface has a ``cylindrical end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $n-1 < -1$~\cite[Section 2.5]{gupta2013meromorphic} \textcolor{orange}{(or cite Aaron's article, which will hopefully present the same background in the translation surface context)}.
\begin{figure}[ht]
    \centering
    %\includegraphics{}
    \caption{On the left an example of translation surface with ``cylindrical end''. On the right, an example of translation surface with  ``$|2n|$-planar end''. }
    \label{fig:translation_surface}
\end{figure}
%
\subsubsection{Direction}\label{transl:dir}
%
The translation structure gives $B$ a notion of direction as well as distance. Away from the zeros of $\lambda$, which we'll call {\em branch points}, we can talk about moving upward, rightward, or at any angle, just as we would on $\C$. At a branch point of cone angle $2\pi n$, we can also talk about moving upward, rightward, or at any angle in $\R/2\pi\Z$, but here there are $n$ directions that fit each description. To make this more concrete, note that around any point $b \in B$, there's a unique holomorphic function $\zeta_b$ that vanishes at $b$ and has $d\zeta_b = \lambda$. \textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] there's a unique translation parameter $\zeta_b$ that vanishes at $b$.} This function is a translation chart when $b$ is an ordinary point, and an $n$-fold branched covering when $b$ is a branch point of cone angle $2\pi n$. In either case, $\zeta_b \in e^{i\theta} [0, \infty)$ is a ray or a set of rays leaving $b$ at angle $\theta \in \R/2\pi\Z$.
%

Near each branch point $b$, let's fix a coordinate $\omega_b$ with $\zeta_b = \tfrac{1}{n} \omega_b^n$, where $2\pi n$ is the cone angle at $b$. This lets us label each direction at $b$ with an ``extended angle'' in $\R/2\pi n\Z$. Of course, there are $n$ different choices for $\omega_b$.
%
\subsubsection{Frequency}\label{transl-freq}
%
The translation structure also gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$ \textcolor{orange}{[make it clear that $z$ is an almost-global chart on $T^*B$---for example, writing $z\colon T^*B\to\C^2$]}. At an ordinary point, we can define $z$ simply as the map
\begin{align*}
z \maps T^*B_b & \to \C \\
\lambda\big|_b & \mapsto 1.
\end{align*}
To get a definition that generalizes to branch points, though, it's worth taking a fancier point of view. Recall that $T^*B_b = \van_b / \van_b^2$, where $\van_b$ is the ideal of holomorphic functions that vanish at $b$. Observing that $(f + \van_b)^n$ lies within $f^n + \van_b^{n+1}$ for any $f \in \van_b$, we can identify $T^*B_b^{\otimes n}$ with $\van_b^n / \van_b^{n+1}$ for $n \ge 1$. When $b$ is an ordinary point, the function $\zeta_b$ defined in Section~\ref{transl:dir} represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda\big|_b$. In general, $\zeta_b$ represents a nonzero element of $\van_b^n / \van_b^{n+1}$, where $2\pi n$ is the cone angle at $b$. We define $z$ as the isomorphism
\begin{align*}
z \maps \van_b^n / \van_b^{n+1} & \to \C \\
\zeta_b + \van^{n+1} & \mapsto 1.
\end{align*}
When $b$ is a branch point, the coordinate $\omega_b$ we chose in Section~\ref{transl:dir} gives us an isomorphism
\begin{align*}
w_b \maps T^*B_b & \to \C \\
\omega_b + \van^2 & \mapsto 1
\end{align*}
that makes the diagram
\begin{center}
\begin{tikzcd}
T^*B_b^{\otimes n} \arrow[r,"z"] & \C \\
T^*B_b \arrow[u,"\blankbox^n"] \arrow[r,"w"'] & \C \arrow[u,"\blankbox^n"']
\end{tikzcd}
\end{center}
commute.
\subsubsection{Boundary}
\textcolor{red}{\textbf{Discuss the visual boundary, citing Lemma~3.1 of Dankwart's thesis \textit{On the large-scale geometry of flat surfaces} for the description of geodesics.}}
%
\subsubsection{The Laplace transform over an ordinary point}\label{laplace:ordinary}
Pick a local holomorphic function $\zeta$ on $B$ with $d\zeta = \lambda$, and an extended angle $\theta \in \R$. \textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] Pick a translation parameter $\zeta$.} The {\em Laplace transform} $\laplace_\zeta^\theta$ turns a local holomorphic function $f$ on $B$ into a local holomorphic function on $T^*B$. When $b \in B$ is an ordinary point, $\laplace_\zeta^\theta f$ is defined on $T_b^*B$ by the formula
\begin{equation}\label{laplace:int}
\laplace_{\zeta}^\theta f\big|_b = \int_{\Gamma_{b}^\theta} e^{-z\zeta} f\,d\zeta,
\end{equation}
where $z$ is the frequency function and $\Gamma_{b}^\theta$ is the ray that leaves $b$ at angle $\theta$. We’ll use the shorthand $\laplace_{\zeta, b}^\theta f := \laplace_\zeta^\theta f \big|_{\zeta = b}$ throughout this document.

@@

\subsubsection{Change of translation chart}\label{sec:change-translation}
Let $b\in B$ be an ordinary point, and let $\zeta_b$ be a coordinate on $B$ so that $\zeta = b + \zeta_b$, then the Laplace transform $\laplace_{\zeta_b,0}$ is defined on $T^*_{b}B$ and it's compatible with $\laplace_{\zeta,b}$.  

@@

Let $\varphi\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$ and for some $\Lambda>0$, then

@@

    \laplace_{\zeta_b, 0} \varphi = e^{b z} \laplace_{\zeta, b} \varphi.

@@

In other words, the diagram 
\begin{center}
 \mathcal{O}(H) \arrow[rr, "e^{bz}"]  &  & e^{zb}\,\mathcal{O}(H)\\
& \singexp{\sigma}{\Lambda}(\Omega_b) \arrow[ul, "\laplace_{\zeta_b,0}"]\arrow[ur,swap,"\laplace_{\zeta,b}"]  &  
\end{center}
commutes, and $H$ is the right half plane $\Re z>0$.

@@

\laplace_{\zeta, b} \varphi & = \int_{\Gamma_{\zeta,b}} e^{-z \zeta}\,\varphi\;d\zeta \\
& = \int_{\Gamma_{\zeta_b,0}} e^{-z(b + \zeta_b)}\,\varphi\;d\zeta_b \\
& = e^{-b z} \int_{\Gamma_{\zeta_b,0}} e^{-z\zeta_b}\,\varphi\;d\zeta_b \\
